Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-07 particle_definitions.tex
Change particle definitions.

\begin{definition}
  A n-dimensional particle, $p$, is an object with zero volume that travels along a n-dimensional path. Traveling along a path means that the particle is at position $\lambda(t)$ at time $t$, for all $t \in [0, T_{f,\lambda}]$. 
\end{definition}

\begin{definition}
A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^n$ and its derivatives at some time $t$.
\end{definition}

\begin{definition}
A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$. We call a condition satisfied if the condition's output is $1$ at time $t$.
\end{definition}

\begin{definition}
A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [0, T_{f, \gamma}]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
\end{definition}

\begin{definition}
  A valid path $\gamma(t)$ for a particle $p$ is a path along which $p$ can travel, such that all its conditions are satisfied at every point along the path.
\end{definition}

\begin{definition}
  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(0) = \bvec{X_1}$ and $\gamma(T_{f, \gamma}) = \bvec{X_2}$.
\end{definition}

@@

>>>>

\begin{definition}
  A n-dimensional path $\gamma(t): \mathrm{R} \to \mathrm{R}^n$ is a function which maps a time $t \in \R$, $t \in [T_0(\gamma), T_f(\gamma)]$, to a position $\bvec{X} \in \mathrm{R}^n$. 
\end{definition}

\begin{definition}
  A particle, $p$, is an object with zero volume that, given a time $t$, can only be located at a position in space. A particle travels along a path, $\gamma(t)$ if the particle is at position $\gamma(t)$ at time $t$, for all $t \in [T_0 (\gamma), T_f(\gamma)]$. If a particle is traveling along a path $\gamma(t)$ ,then we define a position, $\bvec{X} = \gamma(t)$, a velocity, $\bvec{X} = \frac{d\gamma(t)}{dt}$, and an acceleration, $\bvec{X} = \frac{d^2\gamma(t)}{dt^2}$, of the particle, for all $t \in [T_0 (\gamma), T_f(\gamma)]$.

  A particle is restricted, if there are conditions on its position, $\bvec{X}$ and the time derivatives of its position for some $t$. The set of all valid paths for a particle consists of all paths that the particle can travel along.
\end{definition}

\begin{definition}
  A planar path is a 2-dimensional path.
\end{definition}

\begin{definition}
  A path between two points, $\bvec{X_1}$ and $\bvec{X_2}$ is a path, $\gamma(t)$, where $\gamma(T_0(\gamma)) = \bvec{X_1}$ and $\gamma(T_f(\gamma)) = \bvec{X_2}$.
\end{definition}

@@

\begin{definition}
  Constant speed conditions is a set of restrictions on a particle's motion, $\bvec{X}$ in $R^2$, , and its centripetal 
\end{definition}
